Cheminformatics: The Computer Science of Chemical Discovery

### 2011-11-09 rebuttal.tex

\documentclass[11pt,a4paper]{article}
\usepackage{times}

\setlength{\parindent}{0cm}

\begin{document}
\newcommand{\comment}[1]{\textit{``\ldots #1''}\par\vspace{0.5em}}
\newcommand{\response}[1]{#1\vspace{1em}}

\fbox{\textbf{Reviewer 1}}
\
\comment{when the authors state 'together with an even larger number
  of annotations', they shold explain what are annotations and how
  much is the large number;} 
\response{Foo}

\comment{For an overview I would expect a more comprehensive set of
  references.}
\response{We agree with the reviewer that a more comprehensive list of
references would be appropriate and useful. However, due to format
limitations of the article, we have been restricted to the use of XXX
references. To alleviate this problem, we have included a supplement
that provides a more extensive list of references, specifically
including a number of texts covering cheminformatics broadly.}

\fbox{\textbf{Reviewer 2}}

\fbox{\textbf{Reviewer 3}}

\end{document}

### 2011-11-09 paper.tex
Added document for rebuttal. Updated some refs and added them to the suppl history document

Novel technologies in the life sciences churn out information at an ever
increasing rate---public data stores such as the one at the European Bioinformatics
Institute (EBI) contain on the order of 10 petabytes of biological information.
However, while biological information has been publicly available for decades,
the same has not been true for chemical information, until recently. It was
not until 2004 that a large public small molecule structure repository (PubChem)
became freely available. This was followed by other databases, as discussed later
in this article. In the same vein, open source software and the publication of
algorithms have only recently become a main focus of the field
\cite{faulon2010}.

>>>>

Novel technologies in the life sciences churn out information at an
ever increasing rate---public data stores such as the one at the
European Bioinformatics Institute (EBI) contain on the order of 10
petabytes of biological information.  While biological
information has been publicly available for decades, the same has not
been true for chemical information, until recently. It was not until
2004 that a large public small molecule structure repository (PubChem)
became freely available. This was followed by other databases, as
discussed later in this article. In the same vein, open source
software and the publication of algorithms have only recently become a
main focus of the field \cite{faulon2010}.
